Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-12 research_class/paper.tex
Fix typo: subject/verb agreement
Two grammar fixes.

Each Raft node maintains a transaction log. The entries in the
transaction log each contain a term value in addition to the action to
apply to the state machine. Each node also keep track of the most
recent log entry which is known to be committed (exists in the log of
more than half the nodes in the cluster).

When a new leader is elected, it begins sending appendEntries RPCs
to other nodes in the Raft cluster. These RPC messages contain
information about the state of its transaction log: index and term of
the latest entry, and the most recently committed entry. If the node
does not have an entry matching the most recent entry on the leader,
then it replies with false to indicate that its log and not up to
date. The next appendEntries RPC that the leader sends to that
node will contain the next oldest index and term. This will continue
until the leader discovers the latest log entry which is agreement
(the node may not have any entries if it is new). Then the leader will
begin to propagate entries to the node in subsequent appendEntries
RPCs until the node is caught up. The leader continues sending
empty appendEntries as heartbeat RPCs to all the nodes until it
receives a new entry in its transaction log from a client
\cite[Section~3.5]{raft_thesis:ongaro14}.

>>>>

Each Raft node maintains a transaction log. The entries in the
transaction log each contain a term value in addition to the action to
apply to the state machine. Each node also keeps track of the most
recent log entry which is known to be committed (exists in the log of
more than half the nodes in the cluster).

When a new leader is elected, it begins sending appendEntries RPCs
to other nodes in the Raft cluster. These RPC messages contain
information about the state of its transaction log: index and term of
the latest entry, and the most recently committed entry. If the node
does not have an entry matching the most recent entry on the leader,
then it replies with false to indicate that its log is not up to
date. The next appendEntries RPC that the leader sends to that
node will contain the next oldest index and term. This will continue
until the leader discovers the latest log entry which is in agreement
(the node may not have any entries if it is new). Then the leader will
begin to propagate entries to the node in subsequent appendEntries
RPCs until the node is caught up. The leader continues sending
empty appendEntries as heartbeat RPCs to all the nodes until it
receives a new entry in its transaction log from a client
\cite[Section~3.5]{raft_thesis:ongaro14}.
